---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

We are interested in the height of Lake Huron (@fig-height).


```{r}
#| label: fig-height
#| fig-cap: Annual measurements of the level, in feet, of Lake Huron 1875–1972.
#| echo: false

tibble(year = 1875:1972,
       level = as.numeric(datasets::LakeHuron)) |>
  ggplot(aes(x = year, y = level)) +
  labs(x = "Year captured", y = "Height (feet)")+
  geom_point()
```

We are interested in the height of black cherry trees (@fig-treeheight).

```{r}
#| label: fig-treeheight
#| fig-cap: Provides measurements of the height in 31 felled black cherry trees.
#| echo: false

datasets::trees |> 
  as_tibble() |> 
  ggplot(aes(x = Height)) +
  geom_bar() +
  labs(x="Height of tree (feet)", y = "Number of trees") +
  theme_minimal()


```


We are interested in making the penguins graph look bad. (@fig-penguinsbad)

```{r}
#| label: fig-penguinsbad
#| fig-cap: Flipper length and body mass for Adelie, Chinstrap and Gentoo Penguins.
#| echo: false
#| warning: false

ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(size = 100)



```


```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

This is a table of the average speed of light experiments @averagelightspeed

```{r}
#| label: tbl-averagelightspeed
#| tbl-cap: "Michelson data estimating the speed of light (km/sec, with 299000 subtracted), based on five experiemnts in 1879 on the speed of light, averaged over 20 runs" 
#| echo: false

datasets::morley |> 
  tibble() |>
  group_by(Expt) |>
  summarise(average = mean(Speed)) |>
  knitr::kable(
    col.names = c("Experiment Number", "Average Measurement (km/s)"),
    digits = 0
  ) 
  
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 



# Model

The goal of our modelling strategy is twofold. Firstly,...


## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR].


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


